---
title: "Developing Data Products - Shiny Application and pitch slides"
date: "29 Oktober 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Introduction

>- This presentation is the pitch which refers to the shiny web app.
>- The web can can be found here: https://dataproductsfinal.shinyapps.io/developing-data-products-assignment/
>- The presentation and the shiny project was generated using RStudio.


##Description

>- The project has the goal to calculate and estimate the cashflow of properties.
>- You can give some numbers refering to a specific property and the application estimates the cashflow for you.
>- There is no external data needed for this kind of application.
>- You can find all informations and the source code here: https://github.com/michael-gm/dataproducts3


##Server Functions 1/2

```{r, echo = TRUE, eval =FALSE}
calculateRentalYield <- function (weeklyRent, propertyPrice) 
{
  result <- weeklyRent * 52 / propertyPrice * 100
  return(round(result, digits = 2))
}

calculateYearlyCashflow <- function(weeklyRent, strata, council, 
                        water, managementFees, weeklyRepayments)
{
  result <- weeklyRent * 52 - (strata + council + water) * 4 - 
      managementFees * 52 - weeklyRepayments * 52
  return(round(result, digits = 2))
}
```

##Server Functions 2/2

```{r, echo = TRUE, eval =FALSE}

calculateWeeklyCashflow <- function(weeklyRent, strata, council, 
                         water, managementFees, weeklyRepayments)
{
  result <- (weeklyRent * 52 - (strata + council + water) * 4 - 
                 managementFees * 52 - weeklyRepayments * 52) / 52
  return(round(result, digits = 2))
}
```

